Supporting Information

### 2015-08-28 ms.Rmd
switch in situ comparison figure to table

---
title: Genome-wide changes in expression during inflorescence architecture development
  in rice
csl: csl/the-plant-journal.csl
header-includes: \usepackage{graphicx}
output:
  BiocStyle::html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    keep_md: yes
    number_sections: yes
    dev: "CairoPDF"
  word_document:
    fig_caption: yes
    reference_docx: csl/wordStyles.docx
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
bibliography: bib/papersLib.bib
---

>>>>

---
title: Genome-wide changes in expression during inflorescence architecture development
  in rice
csl: csl/the-plant-journal.csl
header-includes: \usepackage{graphicx}
output:
  word_document:
    fig_caption: yes
    reference_docx: csl/wordStyles.docx
  BiocStyle::html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    keep_md: yes
    number_sections: yes
    dev: "CairoPDF"
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
bibliography: bib/papersLib.bib
---

### 2015-08-28 si.Rmd
switch in situ comparison figure to table

**`r I(pasteLabel("Table S", s_tableCount, "st_libStats"))`**: Library and sequencing statistics.

``` {r st_libStats, results = "markup"}
knitr::kable(st_libStats, caption = paste0(
  I(pasteLabel("**Table S", s_tableCount, "st_libStats")),
    "**: Library and sequencing statistics"))
```

@@

# References for SI (citations will be included in *in situ* table)

`r pander::pander(list("85: @Li:2011es", "118: @Ren:2013jv", "129: @Suzaki:2004ib", 
    "21: @Chu:2006fw", "82: @Lee:2012hj", "154: @Yoshida:2013ff", "148: @Xue:2008ki", 
    "3: @Ashikari:2005eg", "150: @Yan:2011hw", "86: @Li:2013iq", "153: @Yoshida:2012fg", 
    "78: @Kurakawa:2007go", "82: @Lee:2012hj", "83: @Lee:2007cj", "48: @Gao:2010iz", 
    "59: @IkedaKawakatsu:2012co", "54: @Horigome:2009gt", "83: @Lee:2007cj", 
    "68: @Jiao:2010ft", "100: @Miura:2010it"))`

>>>>

``` {r st_libStats, results = "asis"}
pander::set.alignment('left', row.names = 'right')
pander::set.caption(paste0(
  I(pasteLabel("**Table S", s_tableCount, "st_libStats")),
  "**: Library and sequencing statistics."))
pander::pandoc.table(st_libStats, split.tables = Inf, emphasize.rownames = FALSE, missing = "")
```

```{r st_reviewInSitu, results = "asis"}
pander::set.alignment('left', row.names = 'right')
pander::set.caption(paste0(
  I(pasteLabel("**Table S", s_tableCount, "st_reviewInSitu")),
  "**: Comparison of the dataset with published *in situ* expression profiles. For each tissue, a '1' indicates that the gene was detected by both methods, a '2' indicates that the gene was detected by *in situ* hybridisation but not by RNA sequencing and a '3' indicates that the gene was detected by RNA sequencing but not reported as expressed by *in situ*. The last category is not informative because *in situ* analysis for the stage in question may have been omitted from the publication. A blank cell indicates that the gene was not detected by either method."))
pander::pandoc.table(st_reviewInSitu, split.tables = Inf, emphasize.rownames = FALSE,
                     emphasize.cols = c(1,2), missing = "")
```

@@

# References for supporting information

labels <- c("1" = "Detected\nin both", "2" = "Only detected\nby in situ", "3" = "Only detected by\nRNA-sequencing")
